\documentclass[]{deedy-resume-openfont}

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\namesection{Rageswari}{Subudhi}{
\custombold{\href{https://drive.google.com/file/d/1-ZlOE-dCxqJ3t8y0GLjmW965CiAVipWH/view}{NET Qualified}}
\custombold{Gate-AIR 155}
\hspace{0.5cm}
\custombold{\urlstyle{same}\href{mailto:subudhi141096@gmail.com}{subudhi141096@gmail.com}} \custombold{\hspace{1cm}+91-9078135156\hspace{1cm}}
\custombold{{\footnotesize D.O.B: } {\normalsize 14/10/1996}}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.30\textwidth}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education}

\subsection{CTAE, MPUAT, Udaipur}
\descript{Ph.D. in Soil \& Water Conservation Engineering}
\location{Expected 2025 | OGPA: 8.78}
\textit{Thesis: Flood Forecasting and Inundation Mapping of Brahmani-Baitarani River Basin for Agricultural Resilience Against Flood}
\sectionsep

\subsection{CTAE, MPUAT, Udaipur}
\descript{M.Tech. in Soil \& Water Conservation Engineering}
\location{July 2021 | OGPA: 8.35 | \textbf{Gold Medalist}}
\textit{Thesis: Development of Iso-Probable Rainfall Map of Rajasthan for Crop Planning}
\sectionsep

\subsection{CAET, OUAT, Bhubaneswar}
\descript{B.Tech. in Agricultural Engineering}
\location{April 2019 | OGPA: 7.98}
\textit{Project: Scope and Opportunities of Water Harvesting in Rainfed Areas}
\sectionsep

\descript{12th CBSE - Science}
\location{Passed 2015 | Bhubaneswar}
Gouri Shankar Residential English Medium School\\
\location{Percentage: 69\%}
\sectionsep

\descript{10th CBSE}
\location{Passed 2013 | Bhubaneswar}
DAV Public School, Pokhariput\\
\location{Percentage: 85.47\%}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links}
LinkedIn: \href{https://www.linkedin.com/in/rageswari-subudhi-250812179/}{\custombold{Rageswari Subudhi}} \\
Research Gate: \href{https://www.researchgate.net/scientific-contributions/2135966431_Rageswari_Subudhi}{\custombold{Rageswari Subudhi}} \\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\begin{tightemize}
\item Urban Hydraulic \& Hydrologic Modeling
\item DPR Preparation for Govt. Projects
\item CAD for Engineering Applications
\item HEC-HMS, HEC-RAS, HEC-SSP, SWAT
\item ArcGIS, QGIS, Google Earth Pro
\item Python, C++, R, MATLAB, SPSS
\item Data Analysis \& Report Writing
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% MEMBERSHIPS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Professional Memberships}
\begin{tightemize}
\item Indian Society of Agricultural Engineers (Life Member since 2019)
\item Indian Association of Soil \& Water Conservationists (Life Member since 2016)
\end{tightemize}
\sectionsep

\end{minipage}
\hfill
\begin{minipage}[t]{0.66\textwidth}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Professional Experience}

\runsubsection{MaRS, Engineering and Private Ltd.}
\descript{| Associate Design Engineer}
\location{Current | Bhubaneswar}
\begin{tightemize}
\item Prepared L-section and base maps for stormwater networks using AutoCAD and GIS tools
\item Guided survey teams for accurate topographic and utility data collection
\item Prepared Detailed Project Reports (DPRs) for Bhubaneswar stormwater drainage under BMC
\item Conducted hydraulic and hydrologic modeling using SWMM/HEC-RAS/StormCAD
\item Designed stormwater network layouts for urban flood mitigation and capacity analysis
\item Presented technical solutions to municipal officials and stakeholders
\end{tightemize}
\sectionsep

\runsubsection{Aquascape Technologies Pvt. Ltd.}
\descript{| Irrigation Designing Engineer \& Project Coordinator}
\location{Current | Bangalore}
\begin{tightemize}
\item Developed efficient irrigation systems with detailed hydraulic plans using CAD software
\item Managed project timelines, budgets, and resources while coordinating with clients
\item Performed site assessments and technical evaluations for irrigation projects
\end{tightemize}
\sectionsep

\runsubsection{Janardan Rai Nagar University}
\descript{| Assistant Professor, Agricultural Engineering}
\location{March 2023 - March 2024 | Udaipur, Rajasthan}
\begin{tightemize}
\item Developed and delivered undergraduate courses in Soil \& Water Conservation Engineering, Farm Machinery \& Power, Greenhouse Technology and Post-harvest Technology
\item Advised and mentored students on academic and career goals
\item Conducted research in Soil and Water Conservation Engineering
\end{tightemize}
\sectionsep

\runsubsection{ICAR Central Institute of Agricultural Engineering}
\descript{| Summer Intern}
\location{July 2018 - August 2018 | Bhopal}
\begin{tightemize}
\item Operation and maintenance of different agro processing equipments
\item Irrigation and drainage engineering
\item Agricultural energy and power
\end{tightemize}
\sectionsep

\section{Awards \& Honors}
\begin{tightemize}
\item NET Qualification, Agricultural Scientists Recruitment Board (2023)
\item Best Paper Award, IASC, Birsa Agricultural University, Ranchi (2022)
\item Best Poster Award, National Conference on Landscape Management for Preventing Flood and Reservoir Sedimentation, BAU, Ranchi (2022)
\item Gold Medal for First in Order of Merit in M.Tech, MPUAT, Udaipur (2021)
\item GATE Qualification (AIR 155), AICTE, MHRD (2019)
\item Second Award, Inter University Dance Competition, CTAE, MPUAT, Udaipur (2020)
\end{tightemize}
\sectionsep

\section{Presentations}
\begin{tightemize}
\item "Combining Hydrological Modeling \& Statistical Analysis for Flood Frequency Assessment in Baitarani River Basin" at 58th ISAE Annual Convention, VNMKV, Parbhani (2024)
\item "Rainfall probability analysis for crop planning in Sirohi district of Rajasthan" at National Conference on Landscape Management for Preventing Flood and Reservoir Sedimentation, BAU, Ranchi (2022)
\item "Water conservation: A necessity of the present to secure the future" at The Institution of Engineers, Kota Local Center, Rajasthan
\item Annual Convention of Indian Society of Agricultural Engineers (ISAE) and International Symposium at Pune
\item "Hydroinformatics for smart water management in Agriculture" at IIT Roorkee
\end{tightemize}
\sectionsep

\section{Selected Publications}
\begin{tightemize}
\item Subudhi, R., Kothari, M., Singh, M., Singh, P.K., \& Chhipa, B.G. (2024). Calibration and Validation of HEC-HMS Model for Baitarani River Basin. \textit{International Journal for Research in Engineering Application \& Management}, 10(09), 35-48. (SJIF Impact Factor: 8.128)
\item Subudhi, R., Kothari, M.S. and Subudhi, C.R. (2021). Rainfall Probability Analysis for Crop Planning in Pratapgarh District of Rajasthan, India. \textit{Int.J.Curr.Microbiol.App.Sci.} 10(08): 611-619. (NAAS score: 5.38)
\item Subudhi, C.R., Senapati, S.C., Subudhi, R., \& Panigrahi, B. (2018). Quantification of runoff, soil loss and yield of crops under different cropping systems in North Eastern ghat Agro-Climatic Zone of Odisha. \textit{Indian Journal of Soil Conservation}, 46(2), 199-205. (NAAS Rating: 4.63)
\item Subudhi, C.R., Senapati, S.C., \& Subudhi, R. (2018). Rain Water Use Efficiency and relationship between rainfall, runoff, soil loss and productivity in Kandhamal district of Odisha. \textit{Journal of Soil and Water Conservation}, 19(1), 54-58. (NAAS rating: 5.51)
\end{tightemize}
\sectionsep

\end{minipage}
\end{document}